### 2023-02-28 paper/content.tex
Add the chi-square formula to the paper's methodology

It's important to note that these are not paleomagnetic declination and
inclination angles, but are instead related to the sample coordinate system. To
obtain the paleomagnetic direction, the dipole moment vector must be rotated to
the sample field orientation prior to the application of
Equation~\ref{eq_vector_to_incdec}.

MISSING PARAGRAPH ABOUT THE COVARIANCE ESTIMATION AND $\sigma_0$.

@@

It is important to note that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters. \cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}). The latter has a maximum value of 1, if \emph{D} is close enough to this value, a simple dipole model is able to explain the measured data. On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data. Some authors \citep[e.g.,][]{Myre2019, CortesOrtuno2021, Lima2009} use another approach for the evaluation of the predicted model, called signal-to-noise ratio (SNR, Eq.~\ref{SNR}). SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor. The higher the SNR (in decibels) values the better it will be the fit of the predicted model. For a signal to be “visible”,  \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise. Thus, both $R^2$ and SNR techniques are appropriate to be used as a criteria filtering for reliability for dipolar inversions.

\begin{equation}
\label{R2}
\begin{aligned}
\large R^2 = 1 - \frac{ {\left( b_z - {b_{z}}_{dipole} \right)}^2 }{{\left( b_z - \bar{b_z} \right)}^2}
\end{aligned}
\end{equation}

>>>>

It is important to note that these are not paleomagnetic declination and inclination angles, but are instead related to the sample coordinate system. To obtain the paleomagnetic direction, the dipole moment vector must be rotated to the sample field orientation prior to the application of Equation~\ref{eq_vector_to_incdec}.

In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies and sensors limitations. This noise added to the observed data vector affects the solution of the estimated parameter vector $\mathbf{m}$, regardless of the method used. Assuming that the noise in the observed data measure is independent and of variance ${\sigma_0}^2$, the latter given by (i) the squared standard deviation used in synthetic cases (e.g., pseudo-random normal distributions) or (ii) the sensor limitations for real samples. Nevertheless, if the sample's variance is not known, one can typically estimate it by using the \emph{$\chi^2$} statistic, \citep[Eq.~\ref{chi_square},][]{Aster2019}, which depends on the residual sum of squares and the degrees of freedom (\emph{v}), the latter being the difference between the number of observed data points (N) and the parameters (m).

\begin{equation}
  \label{chi_square}
\begin{aligned}
\large \sigma_0^2 = {\chi}^2 = \frac{\sum{\left( b_z - {b_{z}}_{dipole} \right)}^2}{N-m}
\end{aligned}
\end{equation}

@@

It is relevant to highlight that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters. \cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}). The latter has a maximum value of 1, if \emph{D} is close enough to this value, a simple dipole model is able to explain the measured data. On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data. Some authors \citep[e.g.,][]{Myre2019, CortesOrtuno2021, Lima2009} use another approach for the evaluation of the predicted model, called signal-to-noise ratio (SNR, Eq.~\ref{SNR}). SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor. The higher the SNR (in decibels) values the better it will be the fit of the predicted model. For a signal to be “visible”,  \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise. Thus, both $R^2$ and SNR techniques are appropriate to be used as a criteria filtering for reliability for dipolar inversions.

\begin{equation}
\label{R2}
\begin{aligned}
\large R^2 = 1 - \frac{ \sum{\left( b_z - {b_{z}}_{dipole} \right)}^2 }{\sum{\left( b_z - \bar{b_z} \right)}^2}
\end{aligned}
\end{equation}
